Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-05-15 eval.tex
Fixed typos.

In this section, we present the results of evaluation of our system. As experimental 
setup, we use RTLSDR together with a signal processing algorithm implemented
in Octave.

@@

In this experiment, we investigate the variation of the television signal
in space, i.e., how does the strength of the signal varies over 
the area of the city. We use the RTLSDR reader to obsevre the signal strength.
We perform the frequency sweep of the desired television band. Next, we
obtain the sample in the time domain, and convert them to corresponding
samples in frequency domain by performing fast-fourier transformation~(FFT).

As we are not interested in realtime visualisation of the television
signals, we acquire the signals offline and visualise the samples.
RTLSDR dongle has a maximum sampling rate of 2.4 MS/s, which limits us to
scanning a band of \SI{1.2}{\mega\hertz} band in a single run. We  keep some safety-margin, and
sample the desired band at \SI{900}{\kilo\hertz} intervals. We sample the band 
\SI{20}{\mega\hertz} wide, by stitching individual bands. In our experiments, it takes roughly 30
seconds for us to perform the scanning operation.

>>>>

In this section, we present the results of evaluation of our system. As experimental 
setup, we use RTL-SDR together with a signal processing algorithm implemented
in Octave.

@@

In this experiment, we investigate the variation of the television signal
in space, i.e., how does the strength of the signal varies over 
the area of the city. We use the RTL-SDR reader to obsevre the signal strength.
We perform the frequency sweep of the desired television band. Next, we
obtain the sample in the time domain, and convert them to corresponding
samples in frequency domain by performing fast-fourier transformation~(FFT).

As we are not interested in realtime visualisation of the television
signals, we acquire the signals offline and visualise the samples.
RTL-SDR has a maximum sampling rate of 2.4 MS/s, which limits us to
scanning a band of \SI{1.2}{\mega\hertz} band in a single run. We  keep some safety-margin, and
sample the desired band at \SI{900}{\kilo\hertz} intervals. We sample the band 
\SI{20}{\mega\hertz} wide, by stitching individual bands. In our experiments, it takes roughly 30
seconds for us to perform the scanning operation.
